Baseline centering problem

### 2018-11-10 paper/advup_uniquesol.tex

>>>>

The TD step in that case is simply
\begin{equation}
\E_s \partial_\theta V(s) \left(
r(s,a)+\gamma(V(s')-V(\tilde s))-V(s)\right)
\end{equation}
ie we just bring $V(s)$ closer to $V(s')-V(\tilde s)$. This is the
simplest trick ever to remove constants...

Would have to check what happens for training $A$, I think we have to
take $\gamma(V(s')-V(\tilde s))-[V(s)-V(\tilde s)]$ if we want to remove
constants on $A$.
